Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-11 content/impl.tex
replacing R with R_IDE; introducing CFG abbreviation

For each program point $n$, the result of an IFDS analysis gives
a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
pairs each such fact~$d$ with a lattice element $\ell$. Formally,
for an IFDS problem $P$, the result $\result_{\text{IFDS}}$ has type
$N \to D$. Similarly, for an IFDS problem $Q$, the result $\result_{\text{IDE}}$
has type $N \to D \times L$.

@@

The output of an IFDS analysis states whether a node is reachable in the exploded supergraph. This means that for an IFDS problem $P$, the IFDS-analysis result $\result_{\text{IFDS}}(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
\begin{equation}
  \result_{\text{IFDS}}(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
\end{equation}

\begin{mdelete}
\begin{example}\label{ex:ifdsresult}
  The solution to the taint-analysis IFDS problem $\mathcal P$ in Listing~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
  \small\begin{align*}
    \result_\text{IFDS}(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
%      
      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
%
      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
%
      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
  \end{align*}\normalsize
  All other nodes of the control-flow supergraph are mapped to the empty set.
\end{example}
\end{mdelete}

 The IDE analysis associates a lattice element with each node in the exploded supergraph. For an IDE problem $Q$, the result $\result(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
\begin{equation}\label{eq:ideresult}
  \result(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
\end{equation}
In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\result(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\result(Q)(n,\,d)=\top$.

@@

The~domain of an equivalence-IDE result 
\begin{equation}
  \resultEq=\result(\transEq(P))
\end{equation}
consists of pairs of control-flow-supergraph nodes and data-flow facts. The range of the result is the set of lattice elements. To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.

\begin{mdelete}
\begin{example}\label{ex:ideresult}
  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
    \small\begin{align*}
    \result(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
      &\dots\}.\\
    \end{align*}\normalsize
  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\result_\text{IFDS}(\mathcal P)$ (see Example~\ref{ex:ifdsresult}). Then $(n,\,d)$ appears in $\result(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
\end{example}
\end{mdelete}

Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
\[
  \rho=\result(\transEq(P)).
\]
For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
\begin{equation}
  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
\end{equation}
Then the transformation function
$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
from an IDE result to~an~IFDS result looks as follows:
\begin{equation}
  \backEq\left(\rho\right)=
    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
\end{equation}

Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result. In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
\begin{equation}
  \backEq\left(\result(\transEq(P))\right)(n)=\result_{\text{IFDS}}(P)(n)\,.
\end{equation}

@@

Let $P$ be an IFDS problem. 
Let $E:\,N\times D$ be the domain of the IDE result $\result(Q)$.
To convert $\result(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\result(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.

For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\result(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
\begin{equation}\label{eq:dnq}
  D_n^\Subset(\rho)=\left\{d\ |\ 
    d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d)(r)\ne\top_T\right\}.
\end{equation}
Then, for a set $S\subseteq R$, the~correlated-calls-conversion function from a~correlated-calls IDE~result $\rho$ to~an~IFDS~result looks as~follows:
\begin{equation}\label{eq:ucc}
  \backCC\left(\rho\right)=
    \left\{(n,\,D_n^\Subset(\rho)\ | \ n\in N^*\right\}.
\end{equation}
}

@@

\begin{lemma}[Precision]\label{lem:subsetifds}
    \otodo{Should we say $\result_{\text{IDE}}$ instead of $\result$ everywhere, to
        be consistent with $\result_{\text{IFDS}}$?}
    For an IFDS problem $P$ and all ${n\in N^*}$,
    \begin{equation}\label{eq:correct}
      \backCC\left(\result(\transCC_R(P))\right)(n)
      \subseteq
      \result_{\text{IFDS}}(P)(n)\,.
    \end{equation}
\end{lemma}

@@

\begin{lemma}[Soundness]\label{lem:sound}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
  If $d\in M_F(p)(\varnothing),$
  then
  \begin{equation}
    d\in \backCC\left(\result(\transCC_R(P))\right)(n)\,.
  \end{equation}
\end{lemma}

@@

\begin{lemma}\label{lem:onlycorrrec}
  Let $P$ be an IFDS problem. Then
  \begin{equation}
    \backCC\left(\result\left(\transCC_\rcc(P)\right)\right)=\backCC(\result\left(\transCC_R(P)\right))\,.
  \end{equation}
\end{lemma}

To summarize, Lemma~\ref{lem:sound} shows that the result $\resultCC$ of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\result_\text{IFDS}$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq=\result_\text{IFDS}$.
Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.

>>>>

For each program point $n$, the result of an IFDS analysis gives
a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
pairs each such fact~$d$ with a lattice element $\ell$. Formally,
for an IFDS problem $P$, the result $\resultIFDS$ has type
$N \to D$. Similarly, for an IFDS problem $Q$, the result $\resultIDE$
has type $N \to D \times L$.

@@

The output of an IFDS analysis states whether a node is reachable in the exploded supergraph. This means that for an IFDS problem $P$, the IFDS-analysis result $\resultIFDS(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
\begin{equation}
  \resultIFDS(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
\end{equation}

\begin{mdelete}
\begin{example}\label{ex:ifdsresult}
  The solution to the taint-analysis IFDS problem $\mathcal P$ in Listing~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
  \small\begin{align*}
    \resultIFDS(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
%      
      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
%
      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
%
      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
  \end{align*}\normalsize
  All other nodes of the control-flow supergraph are mapped to the empty set.
\end{example}
\end{mdelete}

 The IDE analysis associates a lattice element with each node in the exploded supergraph. For an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
\begin{equation}\label{eq:ideresult}
  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
\end{equation}
In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\resultIDE(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\resultIDE(Q)(n,\,d)=\top$.

@@

The~domain of an equivalence-IDE result 
\begin{equation}
  \resultEq=\resultIDE(\transEq(P))
\end{equation}
consists of pairs of control-flow-supergraph nodes and data-flow facts. The range of the result is the set of lattice elements. To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.

\begin{mdelete}
\begin{example}\label{ex:ideresult}
  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
    \small\begin{align*}
    \resultIDE(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
      &\dots\}.\\
    \end{align*}\normalsize
  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\resultIFDS(\mathcal P)$ (see Example~\ref{ex:ifdsresult}). Then $(n,\,d)$ appears in $\resultIDE(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
\end{example}
\end{mdelete}

Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
\[
  \rho=\resultIDE(\transEq(P)).
\]
For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
\begin{equation}
  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
\end{equation}
Then the transformation function
$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
from an IDE result to~an~IFDS result looks as follows:
\begin{equation}
  \backEq\left(\rho\right)=
    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
\end{equation}

Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result. In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
\begin{equation}
  \backEq\left(\resultIDE(\transEq(P))\right)(n)=\resultIFDS(P)(n)\,.
\end{equation}

@@

Let $P$ be an IFDS problem. 
Let $E:\,N\times D$ be the domain of the IDE result $\resultIDE(Q)$.
To convert $\resultIDE(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\resultIDE(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.

For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\resultIDE(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
\begin{equation}\label{eq:dnq}
  D_n^\Subset(\rho)=\left\{d\ |\ 
    d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d)(r)\ne\top_T\right\}.
\end{equation}
Then, for a set $S\subseteq R$, the~correlated-calls-conversion function from a~correlated-calls IDE~result $\rho$ to~an~IFDS~result looks as~follows:
\begin{equation}\label{eq:ucc}
  \backCC\left(\rho\right)=
    \left\{(n,\,D_n^\Subset(\rho)\ | \ n\in N^*\right\}.
\end{equation}
}

@@

\begin{lemma}[Precision]\label{lem:subsetifds}
    For an IFDS problem $P$ and all ${n\in N^*}$,
    \begin{equation}\label{eq:correct}
      \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
      \subseteq
      \resultIFDS(P)(n)\,.
    \end{equation}
\end{lemma}

@@

\begin{lemma}[Soundness]\label{lem:sound}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
  If $d\in M_F(p)(\varnothing),$
  then
  \begin{equation}
    d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
  \end{equation}
\end{lemma}

@@

\begin{lemma}\label{lem:onlycorrrec}
  Let $P$ be an IFDS problem. Then
  \begin{equation}
    \backCC\left(\resultIDE\left(\transCC_\rcc(P)\right)\right)=\backCC(\resultIDE\left(\transCC_R(P)\right))\,.
  \end{equation}
\end{lemma}

To summarize, Lemma~\ref{lem:sound} shows that the result $\resultCC$ of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq$.
Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.

### 2014-12-11 content/intro.tex
figure
replacing R with R_IDE; introducing CFG abbreviation

Data-flow analysis computes an approximation of how values may flow  
through a program, and has applications in compiler optimization, 
programming tools, and computer security, and many other areas.
Data-flow analyses operate on \textit{control-flow graphs} (CFGs)
\mtodo{If we introduce this abbreviation, should we replace the uses of
``control-flow graph'' with ``CFG'' in the paper?}
that model 
the order in which the instructions of a program are executed. This is
typically done by associating \textit{flow functions} that represent how 
data is propagated with the edges of the control-flow graph.  A 
\textit{confluence operator} specifies how the data facts that have been 
computed along different paths should be merged when the paths join.

Since a control-flow graph is an over-approximation of the possible flows 
of control in concrete executions of a program, it may contain \textit{infeasible} 
paths that cannot occur at runtime. The precision of a data-flow analysis algorithm
depends critically on its ability to detect and disregard such infeasible paths.
The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
by  Reps, Horwitz, and Sagiv \cite{reps1995precise} is a general data-flow analysis
algorithm for computing solutions to standard finite distributive data-flow problems such 
as reaching definitions, available expressions, and taint analysis.
\mtodo{We should define somewhere what taint analysis is, since it's currently
commented out.}
A distinguishing 
characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 
and returns to/from functions are not properly matched. Sagiv, Reps, and Horwitz
also presented the \textit{Interprocedural Distributive Environment} (IDE) algorithm
\cite{sagiv1996precise} that similarly only considers properly matched call/return
edges, but that supports a broader range of dataflow problems by expanding the 
domain of flow functions to \textit{environments} that go beyond the data-flow facts 
considered by IFDS.

@@

We present a formalization of the transformation and prove its correctness
as follows. First, we derive an ``Equivalence IDE problem''%
\mtodo{The IDE paper already states that each IFDS problem can be solved with IDE.
I wonder if this sounds like the equivalence transformation was our contribution.
We just use the equivalence transformation to explain the CC transformation, and for the
proofs.
}
from the original 
IFDS problem by associating the identity environment functions with all edges,
and show that the solution to this Equivalence IDE problem can be mapped back
to the solution of the original IFDS problem. Then, we derive a ``Correlated Calls 
IDE Problem'' from the original IFDS problem and show how a solution to this problem 
can be mapped to the solution to the original IFDS problem, but also how a
more precise IFDS result can be derived from it. 
\otodo{Do we need to mention the imprecise map from the CC-IDE result to the IFDS result? It
doesn't really seem relevant, and could be confusing.}
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels $\result$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$ on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\TODO{ref} and that can be ignored here.
}.  
\ftodo{would it make sense to add an edge in Figure~\ref{fig:transformations} from the IFDS problem to the IFDS result?}

>>>>

Data-flow analysis computes an approximation of how values may flow  
through a program, and has applications in compiler optimization, 
programming tools, and computer security, and many other areas.
Data-flow analyses operate on \textit{control-flow graphs} (CFGs)
that model 
the order in which the instructions of a program are executed. This is
typically done by associating \textit{flow functions} that represent how 
data is propagated with the edges of the CFG.  A 
\textit{confluence operator} specifies how the data facts that have been 
computed along different paths should be merged when the paths join.

Since a CFG is an over-approximation of the possible flows 
of control in concrete executions of a program, it may contain \textit{infeasible} 
paths that cannot occur at runtime. The precision of a data-flow analysis algorithm
depends critically on its ability to detect and disregard such infeasible paths.
The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
by  Reps, Horwitz, and Sagiv \cite{reps1995precise} is a general data-flow analysis
algorithm for computing solutions to standard finite distributive data-flow problems such 
as reaching definitions, available expressions, and taint analysis.
A distinguishing 
characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 
and returns to/from functions are not properly matched. Sagiv, Reps, and Horwitz
also presented the \textit{Interprocedural Distributive Environment} (IDE) algorithm
\cite{sagiv1996precise} that similarly only considers properly matched call/return
edges, but that supports a broader range of dataflow problems by expanding the 
domain of flow functions to \textit{environments} that go beyond the data-flow facts 
considered by IFDS.

@@

We present a formalization of the transformation and prove its correctness
as follows. 
First, we derive an IDE problem that is equivalent to the original IFDS problem,
as described by Reps et al.~\cite{sagiv1996precise}.
Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
Then, we derive a ``Correlated Calls 
IDE Problem'' from the original IFDS problem and show 
that the solution to this problem, when converted to an IFDS result, is more precise
than the original IFDS result.
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels $\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
  on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\TODO{ref} and that can be ignored here.
}.\mtodo{In the footnote, should we just say "the labels" since there are so many?}

### 2014-12-11 figures/fig-transformation.tex
replacing R with R_IDE; introducing CFG abbreviation

\begin{figure}
  \centering
    \tikzset{
  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
}
  \tikzstyle{problem}=[fill=greyblue,text width=1.8cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
  \tikzstyle{result}=[fill=bisque,text width=1.5cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
\begin{tikzpicture}
    \node [problem]
      (ifds) {IFDS problem};
    \node [problem]
      (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalent IDE problem};
    \node [problem]
      (ccide)[below=2cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
    \node [result]
      (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
    \node [result]
      (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls IDE result};
    \node [result,text height=1.5cm,text width=2cm]
      (ifdsres) [below right=0cm and \dist of equivres.east] {};
    \node [below,font=\scriptsize] at (ifdsres.north) {IFDS result};
    \node [rounded corners,font=\scriptsize,text width=1.5cm,fill=lightsalmonpink,text=charcoal]
      (improved) [above right=.6cm and (\dist+.3cm) of ccres.east] {Improved IFDS result};

    \path[->] (equivres) edge[out=0,in=150] node[above,font=\scriptsize]{$\backEq$} (ifdsres);
    \path[->] (ccres) edge[out=0,in=230] node[above left,font=\scriptsize] {$\backCC$} (improved);
    %\path[->] (ccres) edge[out=25,in=210] node[above,font=\scriptsize] {$\backEq$} (ifdsres);
    \path[->] (ifds) edge[out=43,in=183] node[above,font=\scriptsize] {$\transEq$} (equiv);
    \path[->] (ifds) edge[out=-45,in=173] node[below,font=\scriptsize] {$\transCC$} (ccide);
    \path[->] (equiv) edge node[above,font=\scriptsize]{$\result$} (equivres);
    \path[->] (ccide) edge node[above,font=\scriptsize]{$\result$} (ccres);
    \path[->,dashed] (ifds) edge[out=-3,in=183] node[above,font=\scriptsize]{$\result_{\text{IFDS}}$} (ifdsres);
\end{tikzpicture}
  \caption{Transformations between IFDS and IDE problems and their results}%
  \label{fig:transformations}%
\end{figure}

>>>>

\begin{figure}
  \centering
    \tikzset{
  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
}
  \tikzstyle{problem}=[fill=greyblue,text width=1.8cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
  \tikzstyle{result}=[fill=bisque,text width=1.5cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
\begin{tikzpicture}
    \node [problem]
      (ifds) {IFDS problem};
    \node [problem]
      (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalence-IDE problem};
    \node [problem]
      (ccide)[below=2cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
    \node [result]
      (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
    \node [result]
      (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls IDE result};
    \node [result,text height=1.5cm,text width=2cm]
      (ifdsres) [below right=0cm and \dist of equivres.east] {};
    \node [below,font=\scriptsize] at (ifdsres.north) {IFDS result};
    \node [rounded corners,font=\scriptsize,text width=1.5cm,fill=lightsalmonpink,text=charcoal]
      (improved) [above right=.6cm and (\dist+.3cm) of ccres.east] {Improved IFDS result};

    \path[->] (equivres) edge[out=0,in=150] node[above,font=\scriptsize]{$\backEq$} (ifdsres);
    \path[->] (ccres) edge[out=0,in=230] node[above left,font=\scriptsize] {$\backCC$} (improved);
    %\path[->] (ccres) edge[out=25,in=210] node[above,font=\scriptsize] {$\backEq$} (ifdsres);
    \path[->] (ifds) edge[out=43,in=183] node[above,font=\scriptsize] {$\transEq$} (equiv);
    \path[->] (ifds) edge[out=-45,in=173] node[below,font=\scriptsize] {$\transCC$} (ccide);
    \path[->] (equiv) edge node[above,font=\scriptsize]{$\resultIDE$} (equivres);
    \path[->] (ccide) edge node[above,font=\scriptsize]{$\resultIDE$} (ccres);
    \path[->,dashed] (ifds) edge[out=-3,in=183] node[above,font=\scriptsize]{$\resultIFDS$} (ifdsres);
\end{tikzpicture}
  \caption{Transformations between IFDS and IDE problems and their results}%
  \label{fig:transformations}%
\end{figure}
